{TestIdeals} package for \emph{Macaulay2}

### 2019-06-16 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Did universal change IsLocal => AtOrigin.

The last option we describe for \texttt{nu} is \texttt{IsLocal}.
Recall that $\nu_I^\idealm(p^e)$ can be interpreted as the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not contained in $\idealm$. 
When computing its value globally, it is the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not the unit ideal.  When 
the value of \texttt{IsLocal} is set to \texttt{false} (from its default value \texttt{true}), then \texttt{nu} instead determines this maximal integer $n$, which can also be characterized as the minimal integer $\nu_I^\mathfrak{n}(p^e)$ as $\mathfrak{n}$ varies among all maximal ideals of the ring.

@@

i37 : nu(1, f, IsLocal => false)

@@

Consider a  $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, whose index not divisible by $p$.
Given a parameter $t \in \mathbb{Q}$ and an element $f$ of $R$, the command \texttt{isFPT(t,f)} outputs \texttt{true} if $t$ is the $F$-pure threshold of $f$, and \texttt{false} otherwise.
Moreover, the function \texttt{compareFPT} provides further information about the relationship between $t$ and the $F$-pure threshold of $f$; namely,
\texttt{compareFPT(t, f)} returns {\tt-1}, \texttt{0}, or \texttt{1} when $t$ is less than, equal to, or greater than, respectively, the $F$-pure threshold of $f$.  Setting the option \texttt{IsLocal} to \texttt{true} tells the function to consider the $F$-pure threshold at the origin.  The following example illustrates this functionality.

@@

i4 : isFPT(1/2, z - 1, IsLocal => true)

@@

Finally, we point out that one can set the option \texttt{IsLocal} from its default value of \texttt{true} to \texttt{false}, to compute the $F$-pure threshold globally. In other words, it computes the minimum of the $F$-pure threshold at all maximal ideals.

@@

i34 : fpt(f, IsLocal => false)

@@

o35 : InfiniteNumber
\end{MyVerbatim}
}
\bigskip
% R = ZZ/7[x,y];
% f = (y-1)^2-(x-1)^3;
% fpt(f, IsLocal => false)
% fpt(f)

@@

The function \texttt{isSimpleNormalCrossing} is exposed to the user, so can be used independent of any $F$-pure threshold calculation.
If the user sets its option \texttt{IsLocal} to \texttt{true} (its default value is \texttt{false}), then the function checks whether the $f_i$ are in simple normal crossing \emph{everywhere}, which can be much slower since Jacobian ideals are computed. Consider the following example illustrating this functionality.

@@

i42 : isSimpleNormalCrossing(f, IsLocal => false)

@@

%             isSimpleNormalCrossing(f, IsLocal=>false)

@@

%             isSimpleNormalCrossing(g, IsLocal=>false)

>>>>

The last option we describe for \texttt{nu} is \texttt{AtOrigin}.
Recall that $\nu_I^\idealm(p^e)$ can be interpreted as the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not contained in $\idealm$. 
When computing its value globally, it is the maximum integer $n$ for which $(I^n)^{[1/p^e]}$ is not the unit ideal.  When 
the value of \texttt{AtOrigin} is set to \texttt{false} (from its default value \texttt{true}), then \texttt{nu} instead determines this maximal integer $n$, which can also be characterized as the minimal integer $\nu_I^\mathfrak{n}(p^e)$ as $\mathfrak{n}$ varies among all maximal ideals of the ring.

@@

i37 : nu(1, f, AtOrigin => false)

@@

Consider a  $\mathbb{Q}$-Gorenstein ring $R$ of characteristic $p>0$, whose index not divisible by $p$.
Given a parameter $t \in \mathbb{Q}$ and an element $f$ of $R$, the command \texttt{isFPT(t,f)} outputs \texttt{true} if $t$ is the $F$-pure threshold of $f$, and \texttt{false} otherwise.
Moreover, the function \texttt{compareFPT} provides further information about the relationship between $t$ and the $F$-pure threshold of $f$; namely,
\texttt{compareFPT(t, f)} returns {\tt-1}, \texttt{0}, or \texttt{1} when $t$ is less than, equal to, or greater than, respectively, the $F$-pure threshold of $f$.  Setting the option \texttt{AtOrigin} to \texttt{true} tells the function to consider the $F$-pure threshold at the origin.  The following example illustrates this functionality.

@@

i4 : isFPT(1/2, z - 1, AtOrigin => true)

@@

Finally, we point out that one can set the option \texttt{AtOrigin} from its default value of \texttt{true} to \texttt{false}, to compute the $F$-pure threshold globally. In other words, it computes the minimum of the $F$-pure threshold at all maximal ideals.

@@

i34 : fpt(f, AtOrigin => false)

@@

o35 : InfiniteNumber
\end{MyVerbatim}
}
\bigskip
% R = ZZ/7[x,y];
% f = (y-1)^2-(x-1)^3;
% fpt(f, AtOrigin => false)
% fpt(f)

@@

The function \texttt{isSimpleNormalCrossing} is exposed to the user, so can be used independent of any $F$-pure threshold calculation.
If the user sets its option \texttt{AtOrigin} to \texttt{true} (its default value is \texttt{false}), then the function checks whether the $f_i$ are in simple normal crossing \emph{everywhere}, which can be much slower since Jacobian ideals are computed. Consider the following example illustrating this functionality.

@@

i42 : isSimpleNormalCrossing(f, AtOrigin => false)

@@

%             isSimpleNormalCrossing(f, AtOrigin=>false)

@@

%             isSimpleNormalCrossing(g, AtOrigin=>false)

### 2019-06-16 Fsing/TestIdealsPaper/TestIdeals.tex
Added a thank to the referees as we ll.
Did universal change IsLocal => AtOrigin.

\subsection*{Acknowledgements}
The authors thank other contributors of the \emph{TestIdeals} package, namely
Erin Bela, Juliette Bruce, Drew Ellingson, Matthew Mastroeni, and Maral Mostafazadehfard.  We also thank Thomas Polstra for pointing out typos in a previous version of this paper.
This paper, and the finishing touches to the \emph{TestIdeals} package, were made at the University of Utah in 2018, and the visiting authors thank the Department of Mathematics for its hospitality.  The authors also thank the referees for their numerous useful comments on both this paper and the code.  Additional work on the package was also done at the Institute of Mathematics and its Applications for its generous support for a 2019 Coding Sprint on the \emph{FThresholds} package.

@@

By default the algorithm checks for $F$-injectivity at all points of $\Spec R$.  However, one
can choose to check $F$-injectivity only at the origin by setting the
option \texttt{IsLocal} to  \texttt{true}.

@@

i3 : isFInjective(R, IsLocal => true) -- but is F-injective at the origin

@@

The default behavior of \texttt{isFRegular} is that it checks for strong $F$-regularity
globally. If the option \texttt{IsLocal} is set to \texttt{true}, the algorithm will only
check $F$-regularity at the origin, by checking whether the computed test ideal is in the irrelevant ideal.
Below are examples for both a ring and a pair.

@@

i3 : isFRegular(R, IsLocal => true) -- but is F-regular at the origin

@@

i7 : isFRegular(5/6, f, IsLocal => true) -- but is F-regular at the origin

@@

The algorithm works by applying Fedder's Criterion {\cite{FedderFPureRat}}, which states that a
local ring $(R, \mathfrak{m})$ is $F$-pure if and only if $(I^{[p]} : I)
\not\subseteq \mathfrak{m}^{[p]}$.
When \texttt{IsLocal} is set to \texttt{true}, the algorithm checks $F$-purity only at the origin, by explicitly checking the above
containment. When \texttt{IsLocal} is set to \texttt{false}, which is its default value, the
algorithm computes the non $F$-pure locus, by applying \texttt{frobeniusRoot}
to $I^{[p]} :I$. If the non $F$-pure locus is the whole ring, the algorithm
returns \texttt{true}.

@@

The options \texttt{AssumeDomain} and \texttt{FrobeniusRootStrategy} can be
used to improve the speed of the \texttt{testModule} computation. By default,
these options are set to \texttt{false} and \texttt{Substitution}, respectively.
Finally, if \texttt{IsLocal} is set to \texttt{true}, then $F$-rationality is checked only at the origin.

>>>>

\subsection*{Acknowledgements}
The authors thank other contributors of the \emph{TestIdeals} package, namely
Erin Bela, Juliette Bruce, Drew Ellingson, Matthew Mastroeni, and Maral Mostafazadehfard.  We also thank the referees as well as Thomas Polstra for pointing out typos in a previous version of this paper.  We also thank the referees for numerous useful comments on the package.
This paper, and the finishing touches to the \emph{TestIdeals} package, were made at the University of Utah in 2018, and the visiting authors thank the Department of Mathematics for its hospitality.  The authors also thank the referees for their numerous useful comments on both this paper and the code.  Additional work on the package was also done at the Institute of Mathematics and its Applications for its generous support for a 2019 Coding Sprint on the \emph{FThresholds} package.

@@

By default the algorithm checks for $F$-injectivity at all points of $\Spec R$.  However, one
can choose to check $F$-injectivity only at the origin by setting the
option \texttt{AtOrigin} to  \texttt{true}.

@@

i3 : isFInjective(R, AtOrigin => true) -- but is F-injective at the origin

@@

The default behavior of \texttt{isFRegular} is that it checks for strong $F$-regularity
globally. If the option \texttt{AtOrigin} is set to \texttt{true}, the algorithm will only
check $F$-regularity at the origin, by checking whether the computed test ideal is in the irrelevant ideal.
Below are examples for both a ring and a pair.

@@

i3 : isFRegular(R, AtOrigin => true) -- but is F-regular at the origin

@@

i7 : isFRegular(5/6, f, AtOrigin => true) -- but is F-regular at the origin

@@

The algorithm works by applying Fedder's Criterion {\cite{FedderFPureRat}}, which states that a
local ring $(R, \mathfrak{m})$ is $F$-pure if and only if $(I^{[p]} : I)
\not\subseteq \mathfrak{m}^{[p]}$.
When \texttt{AtOrigin} is set to \texttt{true}, the algorithm checks $F$-purity only at the origin, by explicitly checking the above
containment. When \texttt{AtOrigin} is set to \texttt{false}, which is its default value, the
algorithm computes the non $F$-pure locus, by applying \texttt{frobeniusRoot}
to $I^{[p]} :I$. If the non $F$-pure locus is the whole ring, the algorithm
returns \texttt{true}.

@@

The options \texttt{AssumeDomain} and \texttt{FrobeniusRootStrategy} can be
used to improve the speed of the \texttt{testModule} computation. By default,
these options are set to \texttt{false} and \texttt{Substitution}, respectively.
Finally, if \texttt{AtOrigin} is set to \texttt{true}, then $F$-rationality is checked only at the origin.

### 2019-06-16 Fsing/TestIdealsPaper/TestIdeals_BACKUP_5127.tex
Did universal change IsLocal => AtOrigin.

By default the algorithm checks for $F$-injectivity everywhere however one can choose to check $F$-injectivity only at the origin by setting the option {\tt IsLocal => true}.
\begin{verbatim}
i2 : R = ZZ/5[x,y,z]/ideal( (x-1)^4 + y^4 + z^4 );
i3 : isFinjective(R)
o3 = false
i4 : isFinjective(R, IsLocal=>true)
o4 = true
\end{verbatim}

@@

The default behavior of {\tt isFregular} checks for strong $F$-regularity everywhere. If the option {\tt IsLocal => true}, the algorithm will only check at the origin (this uses a similar computation but checks for the containment of $(1)$ instead of the test ideal plus the maximal ideal at the origin). Below is an example for both a ring and a pair.

\begin{verbatim}
i2 : R = ZZ/7[x,y,z]/ideal((x-1)^3+(y-2)^3+z^3);
i3 : isFregular(R)
o3 = false
i4 : isFregular(R, IsLocal=>true)
o4 = true
i5 : R = ZZ/13[x,y];
i6 : f = (y-2)^2 - (x-3)^3;
i7 : isFregular(5/6, f)
o7 = false
i8 : isFregular(5/6, f, IsLocal=>true)
o8 = true
\end{verbatim}

>>>>

By default the algorithm checks for $F$-injectivity everywhere however one can choose to check $F$-injectivity only at the origin by setting the option {\tt AtOrigin => true}.
\begin{verbatim}
i2 : R = ZZ/5[x,y,z]/ideal( (x-1)^4 + y^4 + z^4 );
i3 : isFinjective(R)
o3 = false
i4 : isFinjective(R, AtOrigin=>true)
o4 = true
\end{verbatim}

@@

The default behavior of {\tt isFregular} checks for strong $F$-regularity everywhere. If the option {\tt AtOrigin => true}, the algorithm will only check at the origin (this uses a similar computation but checks for the containment of $(1)$ instead of the test ideal plus the maximal ideal at the origin). Below is an example for both a ring and a pair.

\begin{verbatim}
i2 : R = ZZ/7[x,y,z]/ideal((x-1)^3+(y-2)^3+z^3);
i3 : isFregular(R)
o3 = false
i4 : isFregular(R, AtOrigin=>true)
o4 = true
i5 : R = ZZ/13[x,y];
i6 : f = (y-2)^2 - (x-3)^3;
i7 : isFregular(5/6, f)
o7 = false
i8 : isFregular(5/6, f, AtOrigin=>true)
o8 = true
\end{verbatim}
